Conversations in time: interactive visualization to explore structured temporal data

### 2020-08-06 tsibbletalk.Rmd
draft on `plotly_key_tree()`

---
title: "Conversations in time: interactive visualization to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address:
  - Department of Statistics
  - The Univeristy of Auckland
  - New Zealand
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address:
  - Department of Econometrics and Business Statistics
  - Monash University
  - Australia
  email: dicook@monash.edu
bibliography: references.bib
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

@@

Specifying the structure is particularly useful when there's nesting structure in the data.

* Nesting variables generate hierarchical tree, hence `plotly_key_tree()`. Overview and navigation made easier.
* One-to-many linking: marking a single point of interest highlights all other points that share particular data values (categorical linking)
* Lists of key values, and json
* Self-linking: a single data source

>>>>

---
title: "Conversations in time: interactive visualization to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address:
  - Department of Statistics
  - The Univerisity of Auckland
  - New Zealand
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address:
  - Department of Econometrics and Business Statistics
  - Monash University
  - Australia
  email: dicook@monash.edu
bibliography: references.bib
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

@@

Specifying the structure is particularly useful, when there's a hierarchical structure in the data. For such case, a new function `plotly_key_tree()` can help to visualise the "key" structure as a dendrogram, using plotly. This type of plot gives an overview of structured information in the data. Owing to its interactivity, each node in the tree plot is clickable and linked to other plots, and in turn the navigation at various levels is made easier.

When the key structure involves crossing only, one-to-one linking is the default.

* One-to-many linking: marking a single point of interest highlights all other points that share particular data values (categorical linking)
* Constructing recursive lists. Lists of key values, and json
* Self-linking: a single data source

### 2020-08-06 tsibbletalk.tex
draft on `plotly_key_tree()`

Specifying the structure is particularly useful when there's nesting
structure in the data.

\begin{itemize}
\tightlist
\item
  Nesting variables generate hierarchical tree, hence
  \texttt{plotly\_key\_tree()}. Overview and navigation made easier.
\item
  One-to-many linking: marking a single point of interest highlights all
  other points that share particular data values (categorical linking)
\item
  Lists of key values, and json
\item
  Self-linking: a single data source
\end{itemize}

@@

\address{%
Earo Wang\\
The University of Auckland\\
Department of Statistics\\ The Univeristy of Auckland\\ New Zealand\\
}
\href{mailto:earo.wang@auckland.ac.nz}{\nolinkurl{earo.wang@auckland.ac.nz}}

>>>>

Specifying the structure is particularly useful, when there's a
hierarchical structure in the data. For such case, a new function
\texttt{plotly\_key\_tree()} can help to visualise the ``key'' structure
as a dendrogram, using plotly. This type of plot gives an overview of
structured information in the data. Owing to its interactivity, each
node in the tree plot is clickable and linked to other plots, and in
turn the navigation at various levels is made easier.

When the key structure involves crossing only, one-to-one linking is the
default.

\begin{itemize}
\tightlist
\item
  One-to-many linking: marking a single point of interest highlights all
  other points that share particular data values (categorical linking)
\item
  Constructing recursive lists. Lists of key values, and json
\item
  Self-linking: a single data source
\end{itemize}

@@

\address{%
Earo Wang\\
The University of Auckland\\
Department of Statistics\\ The Univerisity of Auckland\\ New Zealand\\
}
\href{mailto:earo.wang@auckland.ac.nz}{\nolinkurl{earo.wang@auckland.ac.nz}}
